Kids stove grades and usage summary

### 2020-07-01 exposure_models.Rmd
analysis updates

# Select analysis vars
selected_vars <- analysis_data %>% 
  #filter(area == "WMT") %>% 
  select(pm_mean_sampling_period, income_3level, area, home,
         residents_smoke,
         home_floors_2level, home_sqft_2level,
         home_pets_2level,
         stove_age_3level, chimney_clean_3level, 
         wood_collect_2level,
         sums_events_sampling_period,
         mean_temp_sampling_period_5,
         amb_pm_sampling_period_5,
         stove_grade_3level,
         home_fireplace) %>% 
  mutate(log_pm_mean_sampling_period = log(pm_mean_sampling_period))   
  select(-pm_mean_sampling_period) %>%

  na.exclude()
```

>>>>

# Select analysis vars
selected_vars <- analysis_data %>% 
  #filter(area == "WMT") %>% 
  select(pm_mean_sampling_period, income_3level, 
         residents_smoke,
         home_floors_2level, home_sqft_2level,
         home_pets_2level,
         stove_age_3level, chimney_clean_3level, 
         wood_collect_2level,
         sums_events_sampling_period,
         mean_temp_sampling_period_5,
         amb_pm_sampling_period_5,
         stove_grade_3level,
         home_fireplace) %>% 
  mutate(log_pm_mean_sampling_period = log(pm_mean_sampling_period)) %>%  
  select(-pm_mean_sampling_period)

  #na.exclude()
```

### 2020-07-01 manuscript_tables_figures.Rmd
analysis updates

char_funct_total("gender_parent")
char_funct_area("gender_parent")
char_funct_total("hispanic_parent")
char_funct_area("hispanic_parent")
char_funct_total("race_parent")
char_funct_area("race_parent")
char_funct_total("education_3level")
char_funct_area("education_3level")
char_funct_total("income_3level")
char_funct_area("income_3level")
char_funct_total("home_floors_2level")
char_funct_area("home_floors_2level")
char_funct_total("home_year_built_2level")
char_funct_area("home_year_built_2level")
char_funct_total("home_pets_2level")
char_funct_area("home_pets_2level")
char_funct_total("stove_age_3level")
char_funct_area("stove_age_3level")
char_funct_total("chimney_clean_3level")
char_funct_area("chimney_clean_3level")
char_funct_total("wood_collect_method_2level")
char_funct_area("wood_collect_method_2level")
char_funct_total("wood_collect_2level")
char_funct_area("wood_collect_2level")
char_funct_total("stove_grade_3level")
char_funct_area("stove_grade_3level")
```

>>>>

char_funct_total("gender_parent")
char_funct_area("gender_parent")
char_funct_total("hispanic_parent")
char_funct_area("hispanic_parent")
char_funct_total("race_parent")
char_funct_area("race_parent")
char_funct_total("education_3level")
char_funct_area("education_3level")
char_funct_total("income_3level")
char_funct_area("income_3level")
char_funct_total("home_floors_2level")
char_funct_area("home_floors_2level")
char_funct_total("home_year_built_2level")
char_funct_area("home_year_built_2level")
char_funct_total("home_pets_2level")
char_funct_area("home_pets_2level")
char_funct_total("stove_age_3level")
char_funct_area("stove_age_3level")
char_funct_total("chimney_clean_3level")
char_funct_area("chimney_clean_3level")
char_funct_total("wood_collect_method_2level")
char_funct_area("wood_collect_method_2level")
char_funct_total("wood_collect_2level")
char_funct_area("wood_collect_2level")
char_funct_total("stove_grade_3level")
char_funct_area("stove_grade_3level")
char_funct_total("ruca_code")
char_funct_area("ruca_code")
char_funct_total("ruca_code_2")
char_funct_area("ruca_code_2")
char_funct_total("ruca_code_3")
char_funct_area("ruca_code_3")
```

### 2020-07-01 merge_datasets.Rmd
analysis updates

analysis_data6 <- stove_grades_clean %>% 
  arrange(area, home, winter_id) %>% 
  group_by(home) %>% 
  mutate(stove_grade = if_else(is.na(stove_grade), lead(stove_grade), stove_grade)) %>% 
  mutate(winter_id = as.character(winter_id)) %>%
  select(area, home, home_winter_id, winter_id, treatment_actual, 
         treatment_assigned, stove_grade) %>% 
  distinct(home, .keep_all = TRUE) %>% 
  right_join(analysis_data5, by = c("area", "home", "home_winter_id", 
                                    "winter_id", "treatment_assigned", 
                                    "treatment_actual")) %>% 
  mutate(stove_grade_3level = fct_collapse(stove_grade,
                                    "A" = "A",
                                    "C" = "C",
                                    "F" = c("D", "F"))) %>% 
  ungroup() %>% 
  arrange(area, home, home_winter_id, sample_date)

@@

         sampling_day, child_id_char, burn_level:mean_temp_roll_4day) %>% 

@@

exposure_analysis_data_short <- exposure_analysis_data_medium %>% 
  group_by(area, home, winter_id) %>% 
  distinct(child_id_char, .keep_all = TRUE) %>% 
  ungroup() %>% 
  arrange(area, home, winter_id)

>>>>

analysis_data6 <- stove_grades_clean %>% 
  arrange(area, home, winter_id) %>% 
  #group_by(home) %>% 
  #mutate(stove_grade = if_else(is.na(stove_grade), lead(stove_grade), stove_grade)) %>% 
  mutate(winter_id = as.character(winter_id)) %>%
  select(area, home, home_winter_id, winter_id, treatment_actual, 
         treatment_assigned, stove_grade) %>% 
  distinct(home, .keep_all = TRUE) %>% 
  right_join(analysis_data5, by = c("area", "home", "home_winter_id", 
                                    "winter_id", "treatment_assigned", 
                                    "treatment_actual")) %>% 
  mutate(stove_grade_3level = fct_collapse(stove_grade,
                                    "A" = "A",
                                    "C" = "C",
                                    "F" = c("D", "F"))) %>% 
  ungroup() %>% 
  arrange(area, home, home_winter_id, sample_date)

@@

  select(area, home, home_id, home_winter_id, winter_id, treatment_assigned, treatment_actual, 
         sampling_day, child_id_char, child_id_num, burn_level:mean_temp_roll_4day) %>% 

@@

exposure_analysis_data_short <- exposure_analysis_data_medium %>% 
  group_by(area, home, winter_id) %>% 
  arrange(area, home, child_id_char, winter_id, sampling_day) %>% 
  distinct(child_id_char, .keep_all = TRUE) %>% 
  ungroup() %>% 
  arrange(area, home, winter_id)

### 2020-07-01 merge_health_datasets.Rmd
analysis updates

health_exposure_data_sampling_day <- health_data_merged %>% 
  select(-pm_mean_sampling_day, -pm_mean_sampling_period) %>% 
  mutate(winter_id = as.character(winter_id)) %>% 
  full_join(exposure_analysis_data_medium,
            by = c("area", "child_id_num", "home", "home_winter_id", "winter_id", 
                   "treatment_assigned", "treatment_actual",
                   "sampling_day")) %>% 
  filter(!is.na(home))

@@

```{r}
health_exposure_data_sampling_day <- 
  read_rds(paste0(file_path, "Output/health_exposure_data_sampling_day.rds"))

>>>>

demographics <- read_rds(paste0(file_path, "Output/demographics_final.rds")) %>% 
  select(child_id_num, child_id_char, area, winter_id)

ruca_mt <- 
  read_xls(paste0(file_path, "Input/ruca2/ruca2_MT.xls")) %>% 
  rename(zip = ZIPN,
         ruca_code = RUCA2) %>% 
  select(zip, ruca_code)

ruca_ak <- 
  read_xls(paste0(file_path, "Input/ruca2/ruca2_AK.xls")) %>% 
  rename(zip = ZIPN,
         ruca_code = RUCA2) %>% 
  select(zip, ruca_code)

ruca_az <- 
  read_xls(paste0(file_path, "Input/ruca2/ruca2_AZ.xls")) %>% 
  rename(zip = ZIPN,
         ruca_code = RUCA2) %>% 
  select(zip, ruca_code)

ruca_nm <- 
  read_xls(paste0(file_path, "Input/ruca2/ruca2_NM.xls")) %>% 
  rename(zip = ZIPN,
         ruca_code = RUCA2) %>% 
  select(zip, ruca_code)

ruca_ut <- 
  read_xls(paste0(file_path, "Input/ruca2/ruca2_UT.xls")) %>% 
  rename(zip = ZIPN,
         ruca_code = RUCA2) %>% 
  select(zip, ruca_code)

ruca_codes <- rbind(ruca_mt, ruca_ak, ruca_az, ruca_nm, ruca_ut)

health_exposure_data_sampling_day <- health_data_merged %>% 
  select(-pm_mean_sampling_day, -pm_mean_sampling_period, -day_of_week,
         -pm_spike_1000, -pm_spike_2000, -pm_spike_5000) %>% 
  mutate(winter_id = as.character(winter_id)) %>% 
  full_join(exposure_analysis_data_medium,
            by = c("area", "child_id_num", "home", "home_winter_id", "winter_id", 
                   "treatment_assigned", "treatment_actual",
                   "sampling_day")) %>% 
  filter(!is.na(home)) %>% 
  filter(!is.na(child_id_num)) %>% 
  select(-child_id_char) %>% 
  left_join(demographics, by = c("area", "winter_id", "child_id_num")) %>% 
  select(area, home, home_id, home_winter_id, winter_id, child_id_num, child_id_char, 
         treatment_assigned, treatment_actual, sampling_day, visit_date:amb_pm_sampling_period_5) %>% 
  left_join(ruca_codes, by = "zip") %>% 
  mutate(ruca_code_2 = if_else(ruca_code >= 10, 10, ruca_code),
         ruca_code_2 = if_else(ruca_code_2 == 7.4, 7, ruca_code_2),
         ruca_code = as.factor(ruca_code),
         ruca_code_2 = as.factor(ruca_code_2),
         ruca_code_3 = fct_collapse(ruca_code_2,
                                    "metro" = c("1", "2"),
                                    "small_town" = c("7", "8", "9"),
                                    "rural" = c("10")))

@@

```{r}
health_exposure_data_sampling_day <- 
  read_rds(paste0(file_path, "Output/health_exposure_data_sampling_day.rds")) %>% 
  select(area, home, zip)

### 2020-07-01 stove_grade_usage_summary.Rmd
analysis updates

stove_grades_total <- stove_grades_clean %>% 
  filter(!is.na(stove_grade)) %>% 
  filter(!is.na(home)) %>% 
  group_by(area, home) %>% 
  distinct(home, .keep_all = TRUE) %>% 
  select(area, home, stove_grade) %>% 
  arrange(area, home) 
```

>>>>

stove_grades_summary <- stove_grades_clean %>% 
  count(area, winter_id, treatment_assigned, stove_grade) 
```
